---
title: "PB Piedmont Output for `r params$BURN_NAME`"
output:
  html_document:
    self_contained: true
    theme: simplex
    toc: false
    css: null
params:
  BURN_NAME: NA
  FOREST: NA
  RUN_ID: NA
  PB_HOURLY_ZIP: NA
  BURN_DATE: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(lubridate)
library(sf)
library(leaflet)
library(leafgl)
library(htmltools)
library(htmlwidgets)
library(lutz)
library(RCurl)
library(rjson)
library(base64enc)
library(jsonlite)
```

```{r data, include=FALSE}
# ---- Find BlueSky output server and burn location ----
serv1_link <- paste0("https://playground-1.airfire.org/bluesky-web-output/", params$RUN_ID, "-dispersion")
serv2_link <- paste0("https://playground-2.airfire.org/bluesky-web-output/", params$RUN_ID, "-dispersion")
serv_links_ls <- list(serv1_link = serv1_link, serv2_link = serv2_link)

date_info_1 <- if (RCurl::url.exists(serv1_link)) {
  tibble(
    server = "serv1_link",
    end_time = lubridate::as_datetime(rjson::fromJSON(file = paste0(serv1_link, "/output.json"))$runtime[["end"]])
  )
} else {
  tibble(server = NA_character_, end_time = as.POSIXct(NA))
}

date_info_2 <- if (RCurl::url.exists(serv2_link)) {
  tibble(
    server = "serv2_link",
    end_time = lubridate::as_datetime(rjson::fromJSON(file = paste0(serv2_link, "/output.json"))$runtime[["end"]])
  )
} else {
  tibble(server = NA_character_, end_time = as.POSIXct(NA))
}

recent_server <- bind_rows(date_info_1, date_info_2) %>%
  filter(!is.na(server)) %>%
  arrange(desc(end_time)) %>%
  slice(1) %>%
  pull(server)

results_output_link <- serv_links_ls[[recent_server]]

burn_info <- read.csv(paste0(results_output_link, "/output/data/fire_locations.csv")) %>%
  dplyr::select(lat = latitude, lon = longitude, utc_offset, date_time) %>%
  mutate(date = lubridate::as_date(lubridate::ymd(date_time)))

burn_tz <- lutz::tz_lookup_coords(
  lat = burn_info$lat[1],
  lon = burn_info$lon[1],
  method = "fast"
)

burn_date <- burn_info$date[1]

fire_icon_uri <- if (file.exists("red-fire-flame.png")) {
  base64enc::dataURI(file = "red-fire-flame.png", mime = "image/png")
} else {
  "https://raw.githubusercontent.com/jeremyash/icons/main/redFlame.png"
}

# ---- Unzip and index PB Piedmont hourly files ----
# IMPORTANT: PB Piedmont hourly filenames are treated as the source of truth.
# Do not convert the filename time into a timezone-aware datetime. The map labels,
# ordering, and filtering below use exactly the date/time text listed in each .txt filename.
stopifnot(!is.null(params$PB_HOURLY_ZIP), file.exists(params$PB_HOURLY_ZIP))

pb_hourly_dir <- tempfile("pb_hourly_")
dir.create(pb_hourly_dir, showWarnings = FALSE, recursive = TRUE)
unzip(params$PB_HOURLY_ZIP, exdir = pb_hourly_dir)

pb_txt_files <- list.files(
  pb_hourly_dir,
  pattern = "^[0-9]{2}[A-Za-z]{3}[0-9]{4}_[0-9]{4}\\.txt$",
  full.names = TRUE,
  recursive = TRUE
)

pb_file_index <- tibble(file = pb_txt_files) %>%
  mutate(
    file_name = basename(file),
    filename_stamp = stringr::str_remove(file_name, "\\.txt$"),
    file_date_text = stringr::str_extract(filename_stamp, "^[0-9]{2}[A-Za-z]{3}[0-9]{4}"),
    file_time_text = stringr::str_extract(filename_stamp, "[0-9]{4}$"),
    file_date = as.Date(stringr::str_to_title(file_date_text), format = "%d%b%Y"),
    file_hour = as.integer(substr(file_time_text, 1, 2)),
    file_minute = as.integer(substr(file_time_text, 3, 4)),
    file_minutes = file_hour * 60 + file_minute,
    file_time_label = paste0(substr(file_time_text, 1, 2), ":", substr(file_time_text, 3, 4)),
    display_label = paste0(format(file_date, "%b %d, %Y"), " ", file_time_label)
  ) %>%
  filter(
    !is.na(file_date),
    !is.na(file_time_text),
    file_time_text >= "0000",
    file_time_text <= "2359"
  ) %>%
  arrange(file_date, file_time_text)

# No time-window filtering here.
# PB Piedmont filename timestamps are treated as the source of truth and are
# used exactly as listed in each .txt filename. This keeps the slider order and
# labels aligned with the uploaded files and avoids timezone conversion issues.
pb_file_index_window <- pb_file_index

if (nrow(pb_file_index_window) == 0) {
  stop("No PB Piedmont hourly text files were found in the uploaded ZIP.")
}

read_pb_particle_file <- function(file) {
  readr::read_table(file, show_col_types = FALSE) %>%
    mutate(
      longitude = as.numeric(longitude),
      latitude = as.numeric(latitude),
      fog = as.integer(fog),
      pt_type = if_else(fog == 1, "Fog", "Smoke"),
      color = if_else(fog == 1, "darkred", "goldenrod")
    ) %>%
    filter(!is.na(longitude), !is.na(latitude), !is.na(fog)) %>%
    sf::st_as_sf(coords = c("longitude", "latitude"), crs = 4326, remove = FALSE)
}

pb_layers <- purrr::map(
  pb_file_index_window$file,
  read_pb_particle_file
)

pb_all <- dplyr::bind_rows(pb_layers) %>% sf::st_drop_geometry()

pb_labels <- pb_file_index_window$display_label
pb_group_names <- paste0("pb-hour-", seq_along(pb_layers))

map_date_label <- if (!all(is.na(params$BURN_DATE))) {
  as.character(params$BURN_DATE)
} else {
  paste0(format(min(pb_file_index_window$file_date, na.rm = TRUE), "%Y-%m-%d"), " to ", format(max(pb_file_index_window$file_date, na.rm = TRUE), "%Y-%m-%d"))
}

map_title <- paste0("PB Piedmont Output for ", params$BURN_NAME, " [", map_date_label, "]")

caution_html <- HTML("Please note: for internal use only.<br>Do not distribute outside of USFS.")
```

<style>
body {
  margin: 0;
  padding: 0;
}

.main-container {
  max-width: none !important;
  width: 100% !important;
  padding: 0 !important;
}

h1.title {
  margin: 0;
  padding: 10px 18px;
  font-size: 22px;
  background: #f8f8f8;
  border-bottom: 1px solid #ddd;
}

.leaflet-container {
  width: 100% !important;
  height: calc(100vh - 58px) !important;
}

.leaflet-control.map-title {
  color: red;
  text-align: left;
  padding: 8px 10px;
  background: rgba(255,255,255,0.75);
  font-weight: bold;
  font-size: 20px;
  border-radius: 4px;
  clear: none !important;
  margin-left: 8px !important;
  margin-top: 10px !important;
}

/* Keep the disclaimer to the right of the +/- zoom buttons. */
.leaflet-left .leaflet-control.map-title {
  float: left !important;
}

.burn-fire-icon {
  width: 30px !important;
  height: 30px !important;
  border-radius: 50%;
  overflow: hidden;
  background: rgba(255,255,255,0.92);
  border: 1px solid rgba(0,0,0,0.35);
  box-shadow: 0 1px 4px rgba(0,0,0,0.35);
}

.burn-fire-icon img {
  width: 24px !important;
  height: 24px !important;
  margin: 3px;
  object-fit: contain;
}

.pb-slider-control {
  background-color: rgba(255,255,255,0.88);
  color: black;
  font-family: Open Sans, sans-serif;
  font-weight: bold;
  padding: 8px 16px 12px 16px;
  border-radius: 5pt;
  box-shadow: 0pt 0pt 6pt 0px rgba(61,59,61,0.48);
  min-width: 340px;
}

.pb-slider-title {
  margin-bottom: 3px;
}

.pb-slider-label {
  font-size: 13px;
  margin-bottom: 4px;
}

.pb-slider-control input[type='range'] {
  width: 300px;
}
</style>

```{r update_browser_title, results='asis', echo=FALSE}
cat(
  paste0(
    "<script>",
    "document.addEventListener('DOMContentLoaded', function() {",
    "  document.title = ", jsonlite::toJSON(map_title, auto_unbox = TRUE), ";",
    "  var h1 = document.querySelector('h1.title');",
    "  if (h1) h1.textContent = ", jsonlite::toJSON(map_title, auto_unbox = TRUE), ";",
    "});",
    "</script>"
  )
)
```

```{r map, out.width='100%'}
# Build a deterministic one-hour-at-a-time canvas map.
# This more closely matches the old Shiny app behavior:
#   filteredData() %>% filter(start_time == input$date[1])
# and then redraws all particles for that selected timestep.

pb_hour_payload <- purrr::map(
  pb_file_index_window$file,
  function(file) {
    readr::read_table(file, show_col_types = FALSE) %>%
      transmute(
        longitude = as.numeric(longitude),
        latitude = as.numeric(latitude),
        fog = as.integer(fog),
        color = if_else(fog == 1, "darkred", "goldenrod")
      ) %>%
      filter(!is.na(longitude), !is.na(latitude), !is.na(fog))
  }
)

pb_map <- leaflet(options = leafletOptions(preferCanvas = TRUE)) %>%
  addProviderTiles(providers$CartoDB.Voyager, group = "Street") %>%
  addProviderTiles("Esri.WorldImagery", group = "Terrain") %>%
  fitBounds(
    lng1 = min(pb_all$longitude, na.rm = TRUE),
    lat1 = min(pb_all$latitude, na.rm = TRUE),
    lng2 = max(pb_all$longitude, na.rm = TRUE),
    lat2 = max(pb_all$latitude, na.rm = TRUE)
  ) %>%
  addLegend(
    "bottomleft",
    colors = c("darkred", "goldenrod"),
    labels = c("Fog", "Smoke"),
    title = "Particle Type",
    opacity = 0.6
  ) %>%
  addScaleBar(position = "bottomright", options = scaleBarOptions(metric = FALSE)) %>%
  addLayersControl(baseGroups = c("Street", "Terrain")) %>%
  addControl(caution_html, position = "topleft", className = "map-title") %>%
  addMarkers(
    data = burn_info,
    lng = ~lon,
    lat = ~lat,
    icon = leaflet::makeIcon(
      iconUrl = fire_icon_uri,
      iconWidth = 30,
      iconHeight = 30,
      iconAnchorX = 15,
      iconAnchorY = 15
    )
  )

pb_map %>%
  htmlwidgets::onRender(
    "
    function(el, x, data) {
      var map = this;
      var currentIndex = 0;
      var canvasRenderer = L.canvas({padding: 0.5});
      var particleLayer = L.layerGroup().addTo(map);

      // Keep the burn icon square/round instead of stretched tall.
      setTimeout(function() {
        var markerImgs = el.querySelectorAll('img.leaflet-marker-icon');
        markerImgs.forEach(function(img) {
          img.style.width = '30px';
          img.style.height = '30px';
          img.style.borderRadius = '50%';
          img.style.objectFit = 'contain';
          img.style.background = 'rgba(255,255,255,0.92)';
          img.style.border = '1px solid rgba(0,0,0,0.35)';
          img.style.boxShadow = '0 1px 4px rgba(0,0,0,0.35)';
          img.style.padding = '3px';
        });
      }, 0);

      function getPointCount(pts) {
        if (Array.isArray(pts)) return pts.length;
        if (pts && Array.isArray(pts.longitude)) return pts.longitude.length;
        return 0;
      }

      function getPoint(pts, i) {
        if (Array.isArray(pts)) return pts[i];
        return {
          longitude: pts.longitude[i],
          latitude: pts.latitude[i],
          color: pts.color[i]
        };
      }

      function redrawParticles(index) {
        particleLayer.clearLayers();
        var pts = data.hours[index] || [];
        var n = getPointCount(pts);

        for (var i = 0; i < n; i++) {
          var p = getPoint(pts, i);
          L.circleMarker([p.latitude, p.longitude], {
            renderer: canvasRenderer,
            radius: 5,
            stroke: false,
            fill: true,
            fillColor: p.color,
            fillOpacity: 0.72,
            interactive: false
          }).addTo(particleLayer);
        }

        currentIndex = index;
        var label = document.getElementById('pb-label-' + el.id);
        if (label) {
          label.innerHTML = data.labels[index];
        }
      }

      var sliderControl = L.control({position: 'bottomleft'});

      sliderControl.onAdd = function(map) {
        var div = L.DomUtil.create('div', 'pb-slider-control leaflet-bar');
        div.innerHTML = `
          <div class='pb-slider-title'>Time step (hour)</div>
          <div class='pb-slider-label' id='pb-label-${el.id}'></div>
          <input id='pb-slider-${el.id}' type='range' min='0' max='${data.hours.length - 1}' value='0' step='1'>
        `;

        L.DomEvent.disableClickPropagation(div);
        L.DomEvent.disableScrollPropagation(div);
        return div;
      };

      sliderControl.addTo(map);

      var slider = document.getElementById('pb-slider-' + el.id);

      slider.addEventListener('input', function(e) {
        redrawParticles(parseInt(e.target.value));
      });

      slider.addEventListener('change', function(e) {
        redrawParticles(parseInt(e.target.value));
      });

      redrawParticles(0);
    }
    ",
    data = list(
      hours = pb_hour_payload,
      labels = pb_labels
    )
  )
```

