---
title: "Smoke Report for `r params$BURN_NAME` Prescribed Fire, `r params$FOREST`"
output:
  html_document: 
    toc: TRUE
    toc_depth: 3
    toc_float: TRUE
    css: report_styles.css
    highlight: null
    self_contained: TRUE
geometry: margin=0.25in
params: 
  BURN_NAME: NA
  REGION: NA
  FOREST: NA
  AUTHOR: NA
  EMAIL: NA
  PHONE: NA
  RUN_ID: NA
  HOURLY_MAP_SELECT: NA 
  FORECAST_AQI_SELECT: NA
  SUPERFOG_SCREEN_SELECT: NA 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

library(tidyverse)
library(RCurl)
library(lubridate)
library(terra)
library(sf)
library(kableExtra)
library(leaflet)
library(rvest)
# library(googlesheets4)
library(lutz)
library(base64enc)
library(htmlwidgets)
library(AirMonitor)

# Embed local/remote images as data URIs so the rendered HTML is self-contained
make_data_uri <- function(path, mime = "image/png") {
  if (file.exists(path)) {
    base64enc::dataURI(file = path, mime = mime)
  } else {
    path
  }
}

download_data_uri <- function(url, mime = "image/png") {
  tmp <- tempfile(fileext = ".png")

  tryCatch(
    {
      curl::curl_download(url, destfile = tmp, quiet = TRUE)
      base64enc::dataURI(file = tmp, mime = mime)
    },
    error = function(e) {
      url
    }
  )
}

fire_icon_uri <- make_data_uri("red-fire-flame.png")
fwd_img_uri <- make_data_uri("fwd.png")
fasm_img_uri <- make_data_uri("fasm.png")

perm_mon_icon_uri <- download_data_uri(
  "https://github.com/jeremyash/icons/blob/main/perm_mon.png?raw=true"
)

temp_mon_icon_uri <- download_data_uri(
  "https://github.com/jeremyash/icons/blob/main/temp_mon.png?raw=true"
)


```

```{r burn_info, include = FALSE}
##***************************************
## FIND MOST RECENT MODEL RUN AND CORRECT SERVER LINK 
##***************************************

# general dispersion results link
bsky_link <- paste("https://tools.airfire.org/playground/v3.5/dispersionresults.php?scenario_id=",
                   params$RUN_ID,
                   sep = "")

# links for results output from both servers
serv1_link <- paste("https://playground-1.airfire.org/bluesky-web-output/",
                      params$RUN_ID,
                      "-dispersion",
                      sep = "")

serv2_link <- paste("https://playground-2.airfire.org/bluesky-web-output/",
                    params$RUN_ID,
                    "-dispersion",
                    sep = "")

serv_links_ls <- list(serv1_link, serv2_link)
names(serv_links_ls) <- c("serv1_link", 
                          "serv2_link")


# get info on end time of simulation for each server
date_info_1 <- if (url.exists(serv1_link)) {
  
  # pull end time from output.json
  end_time_val <- lubridate::as_datetime(jsonlite::fromJSON(file = paste(serv1_link, "/output.json", sep = ""))$runtime[["end"]])
  
  # create df
  end_time_df <- tibble(server = "serv1_link",
                        end_time = end_time_val)
  
}else{
  # create df
  end_time_df <- tibble(server = NA,
                        end_time = NA)}



date_info_2 <- if (url.exists(serv2_link)) {
  
  # pull end time from output.json
  end_time_val <- lubridate::as_datetime(jsonlite::fromJSON(file = paste(serv2_link, "/output.json", sep = ""))$runtime[["end"]])
  
  # create df
  end_time_df <- tibble(server = "serv2_link",
                        end_time = end_time_val)
  
}else{
  # create df
  end_time_df <- tibble(server = NA,
                        end_time = NA)}

# combine outputs, select most recent model and set results_link to correct url
recent_server <- bind_rows(date_info_1, date_info_2) %>% 
  arrange(desc(end_time)) %>% 
  slice(1) %>% 
  pull(server)

results_output_link <- serv_links_ls[[recent_server]]


## CREATE DATAFRAME OF BASIC FIRE INFO  ----------------------------------------------

# basic burn information
basic_burn_info <- read.csv(paste(results_output_link, "/output/data/fire_locations.csv", sep = "")) %>% 
  dplyr::select(lat = latitude,
         lon = longitude,
         utc_offset,
         date_time,
         acres = area,
         consumption_total) %>% 
  mutate(date = as_date(ymd(date_time)),
         consumption_acre = consumption_total/acres)

# generated report timestamp in burn local timezone
burn_tz <- lutz::tz_lookup_coords(
  lat = basic_burn_info$lat[1],
  lon = basic_burn_info$lon[1],
  method = "fast"
)

generated_at <- lubridate::with_tz(Sys.time(), tzone = burn_tz)

generated_at_sen <- paste0(
  "Issued at ",
  format(generated_at, "%H:%M %B %d, %Y"),
  " ",
  format(generated_at, "%Z")
)

# get ignition time
timing_info <- read.csv(paste(results_output_link, "/csvs/fire_emissions.csv", sep = "")) %>% 
  select(date_time, flame_profile) %>% 
  filter(flame_profile!= 0) %>%
  mutate(date_time = as_datetime(date_time) + as.numeric(str_sub(basic_burn_info$utc_offset, start = 1, end=3))*3600) %>% 
  arrange(date_time) %>% 
  mutate(date_time = str_sub(date_time, start = 6)) %>% 
  summarise(flaming_start = min(date_time),
         flaming_end = max(date_time))
  
# burn info combined
burn_info <- basic_burn_info %>% 
  add_column(flaming_start = timing_info$flaming_start,
             flaming_end = timing_info$flaming_end,
             region = params$REGION)

# create sf object of burn location
burn_loc <- burn_info %>% 
  dplyr::select(lon, lat)

# create sf object of burn location
burn_loc_sf <- st_as_sf(burn_loc,
                        coords = c("lon", "lat"),
                        crs = st_crs("EPSG:4326"))

# lat_long value
lat_lon <- paste(burn_info$lat, burn_info$lon, sep = ", ")

# table values
tbf_vals <- burn_info %>% 
  mutate(date = as.character(date)) %>% 
  mutate(consumption_acre = round(consumption_acre, 2)) %>% 
  add_column("lat_lon", lat_lon) %>% 
  select(date, lat_lon, acres, flaming_start, flaming_end, consumption_acre) %>% 
  gather("var", "val")

# generate kable of basic burn information
burn_kable <- tibble(vars = c("Date", "Coordinates", "Acreage", "Flaming Start", "Flaming End", "Consumption (tons/acre)"),
                     vals = tbf_vals$val) %>%
  kbl(col.names = NULL) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  # kable(escape = FALSE, linesep = "", format = "html") %>% 
  column_spec(1, bold = T)


## GENERATE DATA FOR RECENT AIR QUALITY ----------------------------------------------
# start and end dates for pulling air quality monitor data
startdate <- burn_info$date - lubridate::ddays(3)
enddate <- burn_info$date - lubridate::ddays(1)


rec_daily_df <- tryCatch(
  expr = {
    # pull air quality monitoring data and subset to nearest 30 monitors
    near_30 <- 
      # Load latest monitoring data from AirNow
      monitor_loadLatest() %>%
      # Only retain monitors within 300km of the burn
      monitor_filterByDistance(
        longitude = burn_info$lon,
        latitude = burn_info$lat,
        radius = 300000, # 300km
        addToMeta = TRUE
      ) %>%
      # Order monitors by distance from target
      monitor_arrange(distanceFromTarget) %>%
      # Only retain the 30 closest monitors
      monitor_slice_head(30)
    
    # filter to 3 days before burn and get mean values
    near_30_df <- near_30$data %>% 
      # mutate(datetime = ymd(as_date(datetime))) %>% 
      # filter(datetime >= (ymd(as_date(Sys.time())) - 3) & datetime <= (ymd(as_date(Sys.time())) - 1)) %>% 
      
      mutate(datetime = ymd(as_date(datetime))) %>% 
      filter(datetime >= startdate & datetime <= enddate) %>% 
      
      group_by(datetime) %>% 
      summarise_all(.funs = mean, na.rm = TRUE) %>% 
      ungroup() %>% 
      gather(deviceDeploymentID, pm_val, -datetime) %>% 
      mutate(aqi_col = aqiColors(pm_val,
                                 pollutant = c("PM2.5"),
                                 palette = c("EPA")),
             aqi_cat = cut(pm_val, 
                           breaks = US_AQI$breaks_AQI,
                           labels = US_AQI$names_eng)) %>% 
      left_join(., near_30$meta, by = "deviceDeploymentID") %>% 
      mutate(siteName = str_to_title(locationName))
    
    # most recent daily AQI
    rec_daily_df <- near_30_df %>% 
      filter(datetime == max(datetime)) %>% 
      mutate(mon_v5_url = paste0('<a href = "https://tools.airfire.org/monitoring/v5/?centerlat=',
                                 latitude,
                                 '&centerlon=',
                                 longitude,
                                 '&zoom=9&monitors=',
                                 deviceDeploymentID,
                                 '&", target=\"_blank\">',
                                 siteName,
                                 '</a>'))
  },
  error = function(e) {
    logger.error("FAILED TO LOAD MONITORING DATA")
    logger.error(e)
    return(NULL)
  }
)


# subset to separate dfs for permanent and temporary monitors
perm_mon_df <- 
  if ( !(is.null(rec_daily_df)) ) {
    rec_daily_df %>%  
      dplyr::filter(deploymentType == "Permanent")
  } else {
    NULL
  } 

temp_mon_df <- 
  if( !(is.null(rec_daily_df)) ) {
    rec_daily_df %>%
      dplyr::filter(deploymentType == "Temporary")
  } else{
    NULL
  } 


# vector of named AQI colors to assign to airnow polygons; note: needs full spelling of USG
namedColors <- US_AQI$colors_EPA
names(namedColors) <- c(US_AQI$names_eng[1:2], "Unhealthy for Sensitive Groups", US_AQI$names_eng[4:6])

# read in kml of airnow aqi forecast for today
airnow_today <- NULL

tryCatch(
  expr = {
    # NOTE:  This ran into problems in the docker container:  ! object 'Description' not found
    sf <- 
      sf::st_read("https://s3-us-west-1.amazonaws.com/files.airnowtech.org/airnow/today/forecast_today_usa.kml", quiet = TRUE) %>%
      sf::st_zm() %>%
      rowwise()
    
    logger.trace("  names = '%s'", paste0(names(sf), collapse = ", "))
    
    if ( "description" %in% names(sf) ) {
      sf <-
        sf %>%
        mutate(
          aqi_cat = html_text(html_nodes(read_html(description), "i")),
          aqi_color = unname(namedColors[aqi_cat])
        ) %>%
        filter(!(aqi_cat == "Good"))
      airnow_today <- sf
    } else if ( "Description" %in% names(sf) ) {
      sf <-
        sf %>% 
        mutate(
          aqi_cat = html_text(html_nodes(read_html(Description), "i")),
          aqi_color = unname(namedColors[aqi_cat])
        ) %>%
        filter(!(aqi_cat == "Good"))
      airnow_today <- sf
    }
    
  },
  error = function(e) {
    logger.error("FAILED TO LOAD forecast_today_usa.kml")
    logger.error(e)
  }
)

# * airnow_tomorrow ----


# read in kml of airnow aqi forecast for tomorrow
airnow_tomorrow <- NULL

tryCatch(
  expr = {
    # NOTE:  This ran into problems in the docker container:  ! object 'Description' not found
    sf <- 
      sf::st_read("https://s3-us-west-1.amazonaws.com/files.airnowtech.org/airnow/today/forecast_tomorrow_usa.kml", quiet = TRUE) %>%
      sf::st_zm() %>%
      rowwise()
    
    logger.trace("  names = '%s'", paste0(names(sf), collapse = ", "))
    
    if ( "description" %in% names(sf) ) {
      sf <-
        sf %>%
        mutate(
          aqi_cat = html_text(html_nodes(read_html(description), "i")),
          aqi_color = unname(namedColors[aqi_cat])
        ) %>%
        filter(!(aqi_cat == "Good"))
      airnow_tomorrow <- sf
    } else if ( "Description" %in% names(sf) ) {
      sf <-
        sf %>%
        mutate(
          aqi_cat = html_text(html_nodes(read_html(Description), "i")),
          aqi_color = unname(namedColors[aqi_cat])
        ) %>%
        filter(!(aqi_cat == "Good"))
      airnow_tomorrow <- sf
    }
    
  },
  error = function(e) {
    logger.error("FAILED TO LOAD forecast_tomorrow_usa.kml")
    logger.error(e)
  }
)


# create contact info object
contact_info <- tibble(name = if(params$AUTHOR != "") {params$AUTHOR} else{NA},
                       phone = if(params$PHONE != "") {params$PHONE} else{NA},
                       email = if(params$EMAIL != "") {params$EMAIL} else{NA}) %>% 
  select_if(~ !any(is.na(.))) %>% 
  unite("contact", sep=", ") %>% 
  dplyr::pull(contact)


# forecasted AQI statement
forecast_aqi_sen <- if(burn_info$region == "08") {paste("**The forecasted AQI for areas downwind of the planned burn is ",
                                                                      params$FORECAST_AQI_SELECT,
                                                                      ".**",
                                                                      sep = "")} else{""}

# superfog statement
superfog_sen <- ifelse(burn_info$region == "08",
                       ifelse(params$SUPERFOG_SCREEN_SELECT == "Yes",
                              "The spot weather forecast indicates there is potential for superfog formation in the overnight hours. Please see separate modeling output from PB Piedmont to look at nighttime dispersion and areas with elevated chances of superfog formation.",
                              "The spot weather forecast indicates there is not potential for superfog formation in the overnight hours."),
                       "")



```

<div class="report-issued">`r generated_at_sen`</div>


```{=html}
<div class="fire_info_wrapper">
  <div>
    <p class="paragraph">
```

This report documents the recent air quality, smoke analysis and weather forecast for the `r params$BURN_NAME` prescribed fire on the `r params$FOREST`. Dispersion modeling is based on parameters submitted by the requesting unit.

Additional smoke modeling output can be found at the <a href="`r bsky_link`" target="_blank">BlueSky Playground Dispersion Results</a>.

<strong>For more information:</strong>
`r contact_info`

```{=html}
    </p>
  </div>

  <div></div>

  <div>
```

```{r fire_info_tbl, echo=FALSE, warning=FALSE}
burn_kable
```

```{=html}
  </div>
</div>
```


## Recent Air Quality

Shown below is the recently measured air quality index (AQI) in the area. The map shows the burn location and the most recent daily AQI for nearby temporary and permanent monitors. Hover over a monitor of interest and click the name to access additional real-time air quality information and measurements from the last 7 days.

The AQI forecasts for today and tomorrow can be turned on by selecting the layer in the upper right of the map. `r if (!(is.null(params$FORECAST_AQI_SELECT))) forecast_aqi_sen`


```{r burn_map_aqi, out.width="100%", include=TRUE, results='asis'}
## CREATE MAP OF BURN AND NEARBY AQ MONITORS ----------------------------------------------

# read in burn icon for mapping
burn_icon <- tibble(
  x = burn_info$lon,
  y = burn_info$lat,
  image = "red-fire-flame.png"
)

# prep legend
html_legend <- paste0(
  "<img src='", fire_icon_uri, "' style='width:15px;height:15px;'>&nbsp;Burn&nbsp;location<br/>",
  "<img src='", perm_mon_icon_uri, "' style='width:13px;height:13px;'>&nbsp;Permanent&nbsp;monitor<br/>",
  "<img src='", temp_mon_icon_uri, "' style='width:13px;height:13px;'>&nbsp;Temporary&nbsp;monitor<br/>"
)

# function to create color-fillable icons for temp monitors, color coded by AQI
pchIcons <- function(pch = 1, width = 30, height = 30, bg_icon = "black", col = "black", ...) {
  n <- length(pch)
  files <- character(n)
  for (i in seq_len(n)) {
    f <- tempfile(fileext = ".png")
    png(f, width = width, height = height, bg = "transparent")
    par(mar = c(0, 0, 0, 0))
    plot.new()
    points(.5, .5, pch = pch[i], col = col[1], bg = bg_icon[1],
           cex = min(width, height) / 8, ...)
    dev.off()
    files[i] <- base64enc::dataURI(file = f, mime = "image/png")
  }
  files
}

# apply function to temporary monitor data and add to df
temp_mon_df$icons <- if (!(is.null(temp_mon_df))) {
  unlist(lapply(temp_mon_df$aqi_col, function(x) {
    pchIcons(21, 60, 60, bg_icon = x, col = "black", lwd = 2)
  }))
} else {
  NULL
}

# generate base leaflet map
air_mon_leaflet <-
  leaflet() %>%
  addProviderTiles(providers$CartoDB.Voyager) %>%

  addMarkers(
    data = burn_loc, lng = ~lon, lat = ~lat,
    icon = list(
      iconUrl = fire_icon_uri,
      iconWidth = 24,
      iconHeight = 24,
      iconAnchorX = 12,
      iconAnchorY = 12
    )
  ) %>%

  addControl(html = html_legend, position = "bottomleft") %>%

  addLegend(
    colors = US_AQI$colors_EPA,
    labels = US_AQI$names_eng,
    opacity = 0.75,
    title = "AQI",
    position = "bottomleft"
  ) %>%

  fitBounds(
    lng1 = burn_info$lon - 0.5,
    lat1 = burn_info$lat - 0.5,
    lng2 = burn_info$lon + 0.5,
    lat2 = burn_info$lat + 0.5
  ) %>%

  addScaleBar(position = "bottomright")

# conditional add of AQI forecast
air_mon_leaflet <-
  if (is.null(airnow_today) | is.null(airnow_tomorrow)) {
    air_mon_leaflet
  } else {
    air_mon_leaflet %>%
      addPolygons(
        data = airnow_today,
        fillColor = ~aqi_color,
        fillOpacity = 0.75,
        color = ~aqi_color,
        opacity = 0.75,
        group = "Forecast AQI Today"
      ) %>%
      addPolygons(
        data = airnow_tomorrow,
        fillColor = ~aqi_color,
        fillOpacity = 0.75,
        color = ~aqi_color,
        opacity = 0.75,
        group = "Forecast AQI Tomorrow"
      ) %>%
      addLayersControl(
        overlayGroups = c("Forecast AQI Today", "Forecast AQI Tomorrow"),
        options = layersControlOptions(collapsed = FALSE)
      ) %>%
      hideGroup("Forecast AQI Today") %>%
      hideGroup("Forecast AQI Tomorrow")
  }

# conditional add of temporary monitors
air_mon_leaflet <-
  if (!is.null(temp_mon_df) && nrow(temp_mon_df) > 0) {
    air_mon_leaflet %>%
      addMarkers(
        lng = ~longitude,
        lat = ~latitude,
        icon = list(
          iconUrl = ~icons,
          iconSize = c(15, 15)
        ),
        popup = ~mon_v5_url,
        data = temp_mon_df
      )
  } else {
    air_mon_leaflet
  }

# conditional add of permanent monitors
air_mon_leaflet <-
  if (!is.null(perm_mon_df) && nrow(perm_mon_df) > 0) {
    air_mon_leaflet %>%
      addCircleMarkers(
        lng = ~longitude,
        lat = ~latitude,
        fillColor = ~aqi_col,
        fillOpacity = 1,
        stroke = TRUE,
        color = "black",
        popup = ~mon_v5_url,
        radius = 8,
        weight = 1,
        data = perm_mon_df
      )
  } else {
    air_mon_leaflet
  }

# build AQI table HTML
aqi_table <- tibble(
  'Air Quality Index (AQI)' = c("Good", "Moderate", "USG", "Unhealthy", "Very Unhealthy", "Hazardous"),
  'Actions to Protect Yourself' = AirMonitor::US_AQI$actions_eng
) %>%
  kable(
    escape = FALSE,
    linesep = "",
    format = "html"
  ) %>%
  kable_styling(
    full_width = TRUE,
    position = "left",
    bootstrap_options = "condensed"
  ) %>%
  column_spec(
    1,
    width = "28%",
    bold = TRUE,
    color = c("black", "black", "black", "white", "white", "white"),
    background = US_AQI$colors_EPA,
    extra_css = "padding: 4px 10px; line-height: 1.15; font-size: 14px;"
  ) %>%
  column_spec(
    2,
    width = "72%",
    extra_css = "padding: 4px 10px; line-height: 1.15; font-size: 14px;"
  ) %>%
  row_spec(0, extra_css = "padding: 4px 10px; font-size: 14px;") %>%
  row_spec(1:6, extra_css = "height: 28px;") %>%
  as.character()

# ---- MAP (remove bottom spacing) ----
htmltools::div(
  style = "margin-bottom:0;",
  air_mon_leaflet
)

# ---- BOXED TABLE (tight to map) ----
cat(
  paste0(
    "<div style='margin-top:8px; width:100%; max-width:100%; box-sizing:border-box; border:2px solid #cccccc; border-radius:6px; padding:12px 14px; background:#ffffff;'>",
    aqi_table,
    "<div style='margin-top:4px; font-size:14px; line-height:1.3;'>",
    "<strong>Note:</strong> Generally, smoke sensitive people are children and older adults, along with those who have cardiovascular or respiratory conditions. For more smoke and health information: ",
    "<a href='https://fire.airnow.gov/' target='_blank'>https://fire.airnow.gov/</a>",
    "</div>",
    "</div>"
  )
)
```

## Modeled Smoke Dispersion

Below are the smoke modeling outputs for the day of the planned burn. The maps show the **daily average concentrations**, **maximum hourly impact to visual range** and **hourly smoke concentations** for `r burn_info$date`. Zoom in or out on each interactive map to view specific features.


```{r leaflet_map_data_mgt, include=FALSE}

## READ IN POP DATA ----------------------------------------------

# census data
pop <- readRDS("population_aggregate_factor.rds") 


## DOWNLOAD PNG MAP IMAGES AND GRID INFO ----------------------------------------------

# create outlook directory
dir.create("temp", showWarnings = FALSE)
outlook_path <- "temp"

# download daily average PM2.5 PNG
curl::curl_download(
  paste0(
    results_output_link,
    "/output/images-pm25/100m/daily_average/UTC",
    gsub(":", "", burn_info$utc_offset),
    "/GreyColorBar/pm25_100m_daily_average_UTC",
    gsub(":", "", burn_info$utc_offset),
    "_GreyColorBar_",
    burn_info$date_time,
    ".png"
  ),
  destfile = paste0(outlook_path, "/daily_avg.png")
)

# download daily minimum visual range PNG
curl::curl_download(
  paste0(
    results_output_link,
    "/output/images-visualrange/100m/daily_minimum/UTC",
    gsub(":", "", burn_info$utc_offset),
    "/RainbowColorBarVisualRange/visualrange_100m_daily_minimum_UTC",
    gsub(":", "", burn_info$utc_offset),
    "_RainbowColorBarVisualRange_",
    burn_info$date_time,
    ".png"
  ),
  destfile = paste0(outlook_path, "/daily_vis_range.png")
)

# download grid info
curl::curl_download(
  paste0(results_output_link, "/output/grid_info.json"),
  destfile = paste0(outlook_path, "/grid_info.json")
)


## READ PNG FILES ---------------------------------------------------------

grid_info <- jsonlite::fromJSON(paste0(outlook_path, "/grid_info.json"))

# bbox order: xmin, ymin, xmax, ymax
img_bounds <- list(
  xmin = grid_info$bbox[1],
  ymin = grid_info$bbox[2],
  xmax = grid_info$bbox[3],
  ymax = grid_info$bbox[4]
)


avg_png_uri <- base64enc::dataURI(
  file = paste0(outlook_path, "/daily_avg.png"),
  mime = "image/png"
)

vis_png_uri <- base64enc::dataURI(
  file = paste0(outlook_path, "/daily_vis_range.png"),
  mime = "image/png"
)

## HOURLY PM2.5 PNGS ---------------------------------------------------------------

if (params$HOURLY_MAP_SELECT == "Yes") {

  hourly_path <- file.path(outlook_path, "hourly_pm25")
  dir.create(hourly_path, showWarnings = FALSE, recursive = TRUE)

  hourly_png_url <- paste0(
    results_output_link,
    "/output/images-pm25/100m/hourly/GreyColorBar/"
  )

  hourly_png_files <- read_html(hourly_png_url) %>%
    html_elements("a") %>%
    html_attr("href") %>%
    na.omit() %>%
    as.character() %>%
    basename() %>%
    .[grepl("^pm25_100m_hourly_GreyColorBar_[0-9]{12}\\.png$", .)] %>%
    sort()

  hourly_df <- tibble(
    file = hourly_png_files,
    url = paste0(hourly_png_url, hourly_png_files)
  ) %>%
    mutate(
      datetime_str = stringr::str_extract(file, "[0-9]{12}"),
      datetime_local = lubridate::ymd_hm(datetime_str, tz = burn_tz)
    ) %>%
    filter(!is.na(datetime_local)) %>%
    arrange(datetime_local)

  flaming_start_local <- lubridate::ymd_hms(
    paste0(
      lubridate::year(burn_info$date[1]),
      "-",
      burn_info$flaming_start[1]
    ),
    tz = burn_tz
  )

  hourly_df <- hourly_df %>%
    filter(datetime_local >= flaming_start_local - lubridate::hours(1))

  hourly_png_urls <- hourly_df$url

  hourly_labels <- format(
    hourly_df$datetime_local,
    "%H:%M %b %d, %Y"
  )

  # Use online URLs to avoid huge self-contained reports
  hourly_png_data <- hourly_png_urls
}

## PREP POPULATION DATA ----------------------------------------------

# create buffer around ignition to clip SVI/pop rasters
burn_buf <- st_buffer(burn_loc_sf, dist = 500000)

#pop with buffer
pop_cr <- crop(pop, burn_buf, snap="out")                    
pop_fr <- rasterize(burn_buf, pop_cr) 
pop_buf <- mask(x=pop_cr, mask=pop_fr)



## LEAFLET PLOTTING OF DAILY AVERAGE SMOKE AND VISUAL RANGE ----------------------------------------------

# Colors for PM ----------------------------------------------

# colors for pm bins
pm25_cols <- c(
  "#CCE5FFB2",  # 1-9
  "#99CCFFB2",  # 9-35
  "#0D98BAB2",  # 35-55
  "#9ACD32B2",  # 55-150
  "#FFFF00B2",  # 150-250
  "#FF6600B2",  # 250-350
  "#C71585B2",  # 350-500
  "#2B0A78B2"   # >500
)

# bin edges
pm25_bins <- c(1, 9, 35, 55, 150, 250, 350, 500, Inf)


# Colors for Visual Range ----------------------------------------------

# visibility colors
vis_cols <- c(
  "#2B0A78B2",  # 0.00-0.04
  "#722789B2",  # 0.04-0.08
  "#C71585B2",  # 0.08-0.15
  "#FF0000B2",  # 0.15-0.25
  "#FF6600B2",  # 0.25-0.50
  "#FFFF00B2",  # 0.50-1.00
  "#9ACD32B2",  # 1.00-2.00
  "#00FF00B2",  # 2.00-3.00
  "#0D98BAB2",  # 3.00-4.00
  "#0000FFB2",  # 4.00-5.00
  "#99CCFFB2",  # 5.00-20.00
  "#CCE5FFB2",  # 20.00-50.00
  "#FFFFFFB2"   # >50.00
)

vis_bins <- c(0, 0.04, 0.08, 0.15, 0.25, 0.50, 1.00,
              2.00, 3.00, 4.00, 5.00, 20.00, 50.00, Inf)

vis_labels <- c(
  "0-0.04",
  "0.04-0.08",
  "0.08-0.15",
  "0.15-0.25",
  "0.25-0.50",
  "0.50-1",
  "1-2",
  "2-3",
  "3-4",
  "4-5",
  "5-20",
  "20-50",
  ">50"
)


# Colors for Population ----------------------------------------------

# create color palette function for pop
pop_pal_fun <- colorFactor(palette = "magma",
                    levels = levels(pop_buf)[[1]][1]$ID,
                    reverse = TRUE,
                    na.color = "transparent")

# Daily Average Leaflet ----------------------------------------------

# generate leaflet map for average smoke
avg_leaflet <- leaflet() %>% 
  addProviderTiles(providers$CartoDB.Voyager,
                   group = "Street") %>% 

  addProviderTiles("Esri.WorldImagery",
                    group = "Terrain") %>% 
  
  
  # add mappanes to always keep circles, then smoke on top
  addMapPane("pop_map", zIndex = 450) %>%
  addMapPane("smoke_map", zIndex = 460) %>%
  addMapPane("cir_map", zIndex = 470) %>%
  
 addLegend(
    colors = pm25_cols,
    labels = c("1-9", "9-35", "35-55", "55-150", "150-250", "250-350", "350-500", ">500"),
    title = htmltools::HTML("PM<sub>2.5</sub> (&micro;g/m<sup>3</sup>)"),
    opacity = 1
  ) %>%

  # fire location
 addMarkers(data = burn_loc, lng = ~lon, lat = ~lat,
             icon = list(
               iconUrl = fire_icon_uri,
              iconWidth = 24,
                iconHeight = 24,
                iconAnchorX = 12,
                iconAnchorY = 12)) %>% 


  # circular buffers around fire
  addCircles(data = burn_loc, lng = ~lon, lat = ~lat,
             radius = c(402.336, 804.672, 1609.34, 3218.69, 8046.72, 16093.4, 32186.8),
             color = viridis::viridis(7),
             weight = 5,
             opacity = 0.8,
             fill = FALSE,
             group = "Distance from Fire",
           options=gridOptions(pane="cir_map")) %>%

  addLegend(values = c(402.336, 804.672, 1609.34, 3218.69, 8046.72, 16093.4, 32186.8),
           colors = viridis::viridis(7),
           labels = c(0.25, 0.5, 1, 2, 5, 10, 20),
            opacity = 0.75,
           position = "topleft",
           title = "Distance from Fire (miles)",
           group = "Distance from Fire") %>%

  # Pop data
  addRasterImage(pop_buf,
                 colors = pop_pal_fun,
                 opacity = 0.75,
                 group = "Population",
                 options= gridOptions(pane="pop_map")) %>%
  addLegend(pal = pop_pal_fun,
           values = levels(pop_buf)[[1]][1]$ID,
           labFormat  = labelFormat(
             transform = function(x) {
             levels(pop_buf)[[1]]$val[which(levels(pop_buf)[[1]]$ID == x)]}),
            opacity = 0.75,
           position = "topleft",
           title = "Population",
           group = "Population") %>%

  # set scale of map viewer
  fitBounds(lng1 = burn_icon$x - 0.5,
            lat1 = burn_icon$y - 0.5,
            lng2 = burn_icon$x + 0.5,
            lat2 = burn_icon$y + 0.5) %>%

  # scale bar
  addScaleBar(position = "bottomright") %>% 
  

  # add layer control to map
  addLayersControl(
    # overlayGroups = c("Smoke", "Population", "Social Vulnerability Index"),
    overlayGroups = c("Smoke", "Distance from Fire", "Population"),
    baseGroups = c("Street", "Terrain"),
    options = layersControlOptions(zIndex = 490,
                                   collapsed = FALSE)) %>%
  hideGroup("Population") %>%
  hideGroup("Distance from Fire") 

# conditional add of temporary monitors
avg_leaflet <-
  if (!is.null(temp_mon_df) && nrow(temp_mon_df) > 0) {
    avg_leaflet %>%
      addMarkers(
        lng = ~longitude,
        lat = ~latitude,
        icon = list(
          iconUrl = ~icons,
          iconSize = c(15, 15)
        ),
        popup = ~mon_v5_url,
        data = temp_mon_df
      )
  } else {
    avg_leaflet
  }

# conditional add of permanent monitors
avg_leaflet <-
  if (!is.null(perm_mon_df) && nrow(perm_mon_df) > 0) {
    avg_leaflet %>%
      addCircleMarkers(
        lng = ~longitude,
        lat = ~latitude,
        fillColor = ~aqi_col,
        fillOpacity = 1,
        stroke = TRUE,
        color = "black",
        popup = ~mon_v5_url,
        radius = 8,
        weight = 1,
        data = perm_mon_df
      )
  } else {
    avg_leaflet
  }

avg_leaflet <- avg_leaflet %>%
  htmlwidgets::onRender(
    "
    function(el, x, data) {
      var map = this;
      var bounds = [
        [data.ymin, data.xmin],
        [data.ymax, data.xmax]
      ];

      L.imageOverlay(data.url, bounds, {
        opacity: 1,
        pane: 'smoke_map',
        className: 'png-raster-overlay'
      }).addTo(map);
    }
    ",
    data = list(
      url = avg_png_uri,
      xmin = img_bounds$xmin,
      ymin = img_bounds$ymin,
      xmax = img_bounds$xmax,
      ymax = img_bounds$ymax
    )
  )




# generate leaflet map for visual range
vis_leaflet <- leaflet() %>% 
  
addProviderTiles(providers$CartoDB.Voyager) %>% 
  
  addLegend(
    position = "topright",
    colors = vis_cols,
    labels = vis_labels,
    title = "Visual Range (miles)",
    opacity = 1
  ) %>% 
  
  ## fire location
  addMarkers(data = burn_loc, lng = ~lon, lat = ~lat,
             icon = list(
               iconUrl = fire_icon_uri,
                iconWidth = 24,
                iconHeight = 24,
                iconAnchorX = 12,
                iconAnchorY = 12)) %>% 

  
  fitBounds(lng1 = burn_icon$x - 0.5,
            lat1 = burn_icon$y - 0.5,
            lng2 = burn_icon$x + 0.5,
            lat2 = burn_icon$y + 0.5) %>% 
  addScaleBar(position = "bottomright")

vis_leaflet <- vis_leaflet %>%
  htmlwidgets::onRender(
    "
    function(el, x, data) {
      var map = this;
      var bounds = [
        [data.ymin, data.xmin],
        [data.ymax, data.xmax]
      ];

      L.imageOverlay(data.url, bounds, {
        opacity: 1,
        className: 'png-raster-overlay'
      }).addTo(map);
    }
    ",
    data = list(
      url = vis_png_uri,
      xmin = img_bounds$xmin,
      ymin = img_bounds$ymin,
      xmax = img_bounds$xmax,
      ymax = img_bounds$ymax
    )
  )


## Hourly PM2.5 Leaflet ------------------------------------------------------------
if (params$HOURLY_MAP_SELECT == "Yes") {

  fire_icon_uri <- base64enc::dataURI(
    file = "red-fire-flame.png",
    mime = "image/png"
  )

  hourly_leaflet <- leaflet() %>%
    addProviderTiles(providers$CartoDB.Voyager) %>%
    addMapPane("hourly_smoke_map", zIndex = 460) %>%
    addMapPane("hourly_marker_map", zIndex = 700) %>%
    addLegend(
      colors = pm25_cols,
      labels = c("1-9", "9-35", "35-55", "55-150", "150-250", "250-350", "350-500", ">500"),
      title = htmltools::HTML("PM<sub>2.5</sub> (&micro;g/m<sup>3</sup>)"),
      opacity = 1
    ) %>%
    fitBounds(
      lng1 = burn_icon$x - 0.5,
      lat1 = burn_icon$y - 0.5,
      lng2 = burn_icon$x + 0.5,
      lat2 = burn_icon$y + 0.5
    ) %>%
    addScaleBar(position = "bottomright")
  
  # conditional add of temporary monitors
  hourly_leaflet <-
    if (!is.null(temp_mon_df) && nrow(temp_mon_df) > 0) {
      hourly_leaflet %>%
        addMarkers(
          lng = ~longitude,
          lat = ~latitude,
          icon = list(
            iconUrl = ~icons,
            iconSize = c(15, 15)
          ),
          popup = ~mon_v5_url,
          data = temp_mon_df
        )
    } else {
      hourly_leaflet
    }
  
  # conditional add of permanent monitors
  hourly_leaflet <-
    if (!is.null(perm_mon_df) && nrow(perm_mon_df) > 0) {
      hourly_leaflet %>%
        addCircleMarkers(
          lng = ~longitude,
          lat = ~latitude,
          fillColor = ~aqi_col,
          fillOpacity = 1,
          stroke = TRUE,
          color = "black",
          popup = ~mon_v5_url,
          radius = 8,
          weight = 1,
          data = perm_mon_df
        )
    } else {
      hourly_leaflet
    }
    
  hourly_leaflet <- hourly_leaflet %>% 
    htmlwidgets::onRender(
      "
      function(el, x, data) {
        var map = this;

        var bounds = [
          [data.ymin, data.xmin],
          [data.ymax, data.xmax]
        ];

        var overlays = data.urls.map(function(url) {
          return L.imageOverlay(url, bounds, {
            opacity: 1,
            pane: 'hourly_smoke_map',
            className: 'png-raster-overlay'
          });
        });

        var currentIndex = 0;
        overlays[currentIndex].addTo(map);

        var fireIcon = L.icon({
          iconUrl: data.fire_icon,
          iconSize: [24, 24],
          iconAnchor: [12, 12]
        });

        L.marker([data.burn_lat, data.burn_lon], {
          icon: fireIcon,
          zIndexOffset: 10000
        }).addTo(map);

        var sliderControl = L.control({position: 'bottomleft'});

        sliderControl.onAdd = function(map) {
          var div = L.DomUtil.create('div', 'hourly-slider-control leaflet-bar');
          div.innerHTML = `
            <div class='hourly-slider-title'>Hourly PM<sub>2.5</sub></div>
            <div class='hourly-slider-label' id='hourly-label-${el.id}'>${data.labels[0]}</div>
            <input id='hourly-slider-${el.id}' type='range' min='0' max='${data.urls.length - 1}' value='0' step='1'>
          `;

          L.DomEvent.disableClickPropagation(div);
          L.DomEvent.disableScrollPropagation(div);

          return div;
        };

        sliderControl.addTo(map);

        var slider = document.getElementById('hourly-slider-' + el.id);
        var label = document.getElementById('hourly-label-' + el.id);

        slider.addEventListener('input', function(e) {
          var newIndex = parseInt(e.target.value);

          if (map.hasLayer(overlays[currentIndex])) {
            map.removeLayer(overlays[currentIndex]);
          }

          overlays[newIndex].addTo(map);
          currentIndex = newIndex;
          label.innerHTML = data.labels[newIndex];
        });
      }
      ",
      data = list(
        urls = hourly_png_data,
        labels = hourly_labels,
        xmin = img_bounds$xmin,
        ymin = img_bounds$ymin,
        xmax = img_bounds$xmax,
        ymax = img_bounds$ymax,
        burn_lon = burn_loc$lon[1],
        burn_lat = burn_loc$lat[1],
        fire_icon = fire_icon_uri
      )
    )
}


# remove smoke dispersion files from directory
unlink(outlook_path,
       recursive = TRUE)
```

### Average Daily Smoke Conditions

The average daily smoke conditions are helpful for concerns related to public health. Select **Population** to see the number of people in each census tract surrounding the planned burn.

```{r avg_leaflet_map_show, out.width="100%", include=TRUE}
avg_leaflet
```


### Maximum Hourly Impact to Visual Range

The maximum hourly impact to visual range shows estimated smoke impacts to visibility in the area. This map is useful for identifying potential impacts to visibility on roadways or other sensitive areas.

```{r vis_leaflet_map_show, out.width="100%", include=TRUE}
vis_leaflet
```


```{r hourly_leaflet_text, results='asis', echo=FALSE, eval=params$HOURLY_MAP_SELECT == "Yes"}
cat("### Hourly Smoke Conditions\n\n")
cat("Use the slider on the map to view the hourly modeled smoke concentrations from the time of ignition.\n\n")
```

```{r hourly_leaflet_map_show, out.width="100%", echo=FALSE, eval=params$HOURLY_MAP_SELECT == "Yes"}
hourly_leaflet
```

```{r superfog_section, results='asis'}
if (params$REGION == "08") {
  cat("## Superfog Screening\n\n")
  cat(superfog_sen, "\n")
}
```



## Meteorological and Air Quality Conditions

The Fire Weather Dashboard link below shows predicted fire weather for the area. The Fire and Smoke Map shows air quality conditions and is a valuable resource for monitoring smoke impacts throughout the day.


```{r firepoker_link, include=FALSE}

## Generate Fire Weather Dashboard link
fwd_url <- paste0("https://www.weather.gov/dlh/fwd?lat=",
                  round(burn_loc$lat, 3),
                  "&lon=",
                  round(burn_loc$lon, 3),
                  "&clat=38.967&clon=-97.267&zoom=7.000&basemap=stamenterrain&bbox=[-16540299.098,2518065.675,-5115162.882,6915872.719]&layers=USStates|ForecastDot|Domain|SurfaceFronts|Radar|&fwf=F&dispersion=0,13,30,60,250&ndfd=windgust&nohelp=t&vrunits=ktft")

## Generate Fire and Smoke Map Link
fasm_url <- paste0("https://fire.airnow.gov/#6.91/",
                   round(burn_loc$lat, 3),
                  "/",
                  round(burn_loc$lon, 3))

```

```{=html}
<style>
.link-card-wrap {
  display: flex;
  gap: 18px;
  width: 100%;
  margin: 18px 0;
}

.link-card {
  position: relative;
  flex: 1;
  height: 220px;
  overflow: hidden;
  border-radius: 8px;
  border: 1px solid #cccccc;
  background: #000000;
}

.link-card img {
  width: 100%;
  height: 100%;
  object-fit: cover;
  opacity: 0.45;
}

.link-card a {
  position: absolute;
  inset: 0;
  display: flex;
  align-items: center;
  justify-content: center;
  color: white !important;
  font-size: 26px;
  font-weight: 700;
  text-align: center;
  text-decoration: none;
  padding: 14px;
}

.link-card a:hover {
  text-decoration: underline;
}

@media (max-width: 700px) {
  .link-card-wrap {
    flex-direction: column;
  }

  .link-card {
    height: 190px;
  }
}
</style>
```

```{r weather_link_cards, results='asis'}
cat(
  paste0(
    '<div class="link-card-wrap">',

      '<div class="link-card">',
        '<img src="', fwd_img_uri, '" alt="Fire Weather Dashboard">',
        '<a href="', fwd_url, '" target="_blank">Fire Weather Dashboard</a>',
      '</div>',

      '<div class="link-card">',
        '<img src="', fasm_img_uri, '" alt="Fire and Smoke Map">',
        '<a href="', fasm_url, '" target="_blank">Fire and Smoke Map</a>',
      '</div>',

    '</div>'
  )
)
```



```{r smoke_report_logs, include = FALSE, echo = FALSE, message = FALSE}

# tryCatch(
#     expr = {
#       # set up authentication to write to google sheet
#       googledrive::drive_auth(path = ".secrets/smoke-report-logs-7ae50f5a86d1.json")
#       gs4_auth(path = ".secrets/smoke-report-logs-7ae50f5a86d1.json")
#       
#       # log sheet location
#       log_url <- "https://docs.google.com/spreadsheets/d/1MR94IFlQSbBQ5mbh1nfnyPwT9Eu0GACjquya7rlg1KE/edit?gid=0#gid=0"
#       
#       # superfog data to log
#       superfog_log <- ifelse(burn_info$region == "08",
#                              ifelse(params$SUPERFOG_SCREEN_SELECT == "Yes",
#                                     "Yes",
#                                     "No"),
#                              NA)
#       
#       # data before or of burn to log
#       day_log <- ifelse(burn_info$region == "09",
#                              ifelse(params$DAY_BEFORE_OF_SELECT == "Day before",
#                                     "Day before",
#                                     "Day of"),
#                              NA)
#       
#       
#       # data to log
#       model_run_df <- data.frame(
#         "Region" = burn_region,            
#         "Forest" = params$FOREST,          
#         "Burn Unit" = params$BURN_NAME,       
#         "Burn Date" = burn_info$date,
#         "Date Issued" = Sys.Date(), 
#         "Latitude" = burn_info$lat,        
#         "Longitude" = burn_info$lon,        
#         "Acreage" = burn_info$acres,         
#         "PG Link" = bsky_link,          
#         "Superfog Potential" = superfog_log,         
#         "Day before or of" = day_log
#       )
#       
#       
#       # write data to google sheets log
#       sheet_append(log_url, model_run_df, sheet = 1)
#     },
#     
#     error = function(e) {
#       logger.error("FAILED TO WRITE DATA TO GOOGLE SHEETS")
#       logger.error(e)
#       return(NULL) 
#     }
#   )

```