---
title: ""
output:
  html_document:
    self_contained: true
    theme: simplex
    toc: false
    css: null
params:
  BURN_NAME: NA
  FOREST: NA
  RUN_ID: NA
  PB_HOURLY_ZIP: NA
  BURN_DATE: NA
  BURN_LAT: NA
  BURN_LON: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(lubridate)
library(sf)
library(leaflet)
library(leafgl)
library(htmltools)
library(htmlwidgets)
library(lutz)
library(RCurl)
library(rjson)
library(base64enc)
library(jsonlite)
library(here)
```


```{r data, include=FALSE}
# ---- Burn location ----
# The smoke-report workflow can provide a BlueSky RUN_ID and pull the burn
# location from fire_locations.csv. The standalone PB Piedmont workflow can
# provide BURN_LAT/BURN_LON directly and does not require a BlueSky run.
run_id_available <- (
  !is.null(params$RUN_ID) &&
    !is.na(params$RUN_ID) &&
    nzchar(as.character(params$RUN_ID))
)

manual_location_available <- (
  !is.null(params$BURN_LAT) &&
    !is.na(params$BURN_LAT) &&
    !is.null(params$BURN_LON) &&
    !is.na(params$BURN_LON)
)

if (manual_location_available) {

  burn_info <- tibble(
    lat = as.numeric(params$BURN_LAT),
    lon = as.numeric(params$BURN_LON),
    utc_offset = NA_character_,
    date_time = NA_character_,
    date = as.Date(NA)
  )

} else if (run_id_available) {

  serv1_link <- paste0("https://playground-1.airfire.org/bluesky-web-output/", params$RUN_ID, "-dispersion")
  serv2_link <- paste0("https://playground-2.airfire.org/bluesky-web-output/", params$RUN_ID, "-dispersion")
  serv_links_ls <- list(serv1_link = serv1_link, serv2_link = serv2_link)

  date_info_1 <- if (RCurl::url.exists(serv1_link)) {
    tibble(
      server = "serv1_link",
      end_time = lubridate::as_datetime(rjson::fromJSON(file = paste0(serv1_link, "/output.json"))$runtime[["end"]])
    )
  } else {
    tibble(server = NA_character_, end_time = as.POSIXct(NA))
  }

  date_info_2 <- if (RCurl::url.exists(serv2_link)) {
    tibble(
      server = "serv2_link",
      end_time = lubridate::as_datetime(rjson::fromJSON(file = paste0(serv2_link, "/output.json"))$runtime[["end"]])
    )
  } else {
    tibble(server = NA_character_, end_time = as.POSIXct(NA))
  }

  recent_server <- bind_rows(date_info_1, date_info_2) %>%
    filter(!is.na(server)) %>%
    arrange(desc(end_time)) %>%
    slice(1) %>%
    pull(server)

  if (length(recent_server) == 0 || is.na(recent_server)) {
    stop("Unable to find BlueSky output for RUN_ID, and no manual burn lat/lon was provided.")
  }

  results_output_link <- serv_links_ls[[recent_server]]

  burn_info <- read.csv(paste0(results_output_link, "/output/data/fire_locations.csv")) %>%
    dplyr::select(lat = latitude, lon = longitude, utc_offset, date_time) %>%
    mutate(date = lubridate::as_date(lubridate::ymd(date_time)))

} else {
  stop("PB Piedmont map requires either BURN_LAT/BURN_LON or a valid RUN_ID.")
}

burn_tz <- tryCatch(
  lutz::tz_lookup_coords(
    lat = burn_info$lat[1],
    lon = burn_info$lon[1],
    method = "fast"
  ),
  error = function(e) NA_character_
)

# PB Piedmont filenames are UTC. Convert them to the burn-local timezone
# determined from the burn coordinates. If timezone lookup fails, keep UTC
# rather than stopping report generation.
if (is.na(burn_tz) || !nzchar(burn_tz)) {
  burn_tz <- "UTC"
}

burn_date <- burn_info$date[1]

fire_icon_file <- here::here(
  "assets",
  "red-fire-flame.png"
)

fire_icon_uri <- if (file.exists(fire_icon_file)) {
  base64enc::dataURI(
    file = fire_icon_file,
    mime = "image/png"
  )
} else {
  "https://raw.githubusercontent.com/jeremyash/icons/main/redFlame.png"
}

pb_icon_file <- here::here(
  "www",
  "pb_fog_icon.svg"
)

pb_icon_uri <- if (file.exists(pb_icon_file)) {
  base64enc::dataURI(
    file = pb_icon_file,
    mime = "image/svg+xml"
  )
} else {
  ""
}
# ---- Unzip and index PB Piedmont hourly files ----
# IMPORTANT: PB Piedmont hourly filenames are UTC timestamps.
# The filenames remain the source of truth for ordering, but slider labels
# are converted from UTC into the burn-local timezone determined above.
stopifnot(!is.null(params$PB_HOURLY_ZIP), file.exists(params$PB_HOURLY_ZIP))

pb_hourly_dir <- tempfile("pb_hourly_")
dir.create(pb_hourly_dir, showWarnings = FALSE, recursive = TRUE)
unzip(params$PB_HOURLY_ZIP, exdir = pb_hourly_dir)

pb_txt_files <- list.files(
  pb_hourly_dir,
  pattern = "^[0-9]{2}[A-Za-z]{3}[0-9]{4}_[0-9]{4}\\.txt$",
  full.names = TRUE,
  recursive = TRUE
)

pb_file_index <- tibble(file = pb_txt_files) %>%
  mutate(
    file_name = basename(file),
    filename_stamp = stringr::str_remove(file_name, "\\.txt$"),
    file_date_text = stringr::str_extract(filename_stamp, "^[0-9]{2}[A-Za-z]{3}[0-9]{4}"),
    file_time_text = stringr::str_extract(filename_stamp, "[0-9]{4}$"),

    # Parse the filename timestamp as UTC.
    file_datetime_utc = as.POSIXct(
      stringr::str_to_title(filename_stamp),
      format = "%d%b%Y_%H%M",
      tz = "UTC"
    ),

    # Convert UTC filename timestamp to local burn timezone for display.
    file_datetime_local = lubridate::with_tz(file_datetime_utc, tzone = burn_tz),

    file_date_utc = as.Date(file_datetime_utc),
    file_date_local = as.Date(file_datetime_local),
    utc_time_label = format(file_datetime_utc, "%H:%M UTC"),
    local_time_label = format(file_datetime_local, "%H:%M %Z"),
    display_label = paste0(
      format(file_datetime_local, "%b %d, %Y"),
      " ",
      local_time_label
    )
  ) %>%
  filter(!is.na(file_datetime_utc)) %>%
  arrange(file_datetime_utc)

# No time-window filtering here. Include every hourly .txt file in the ZIP.
# Ordering is by UTC filename timestamp; display labels are burn-local time.
pb_file_index_window <- pb_file_index

if (nrow(pb_file_index_window) == 0) {
  stop("No PB Piedmont hourly text files were found in the uploaded ZIP.")
}

read_pb_particle_file <- function(file) {
  readr::read_table(file, show_col_types = FALSE) %>%
    mutate(
      longitude = as.numeric(longitude),
      latitude = as.numeric(latitude),
      fog = as.integer(fog),
      pt_type = if_else(fog == 1, "Fog", "Smoke"),
      color = if_else(fog == 1, "darkred", "goldenrod")
    ) %>%
    filter(!is.na(longitude), !is.na(latitude), !is.na(fog)) %>%
    sf::st_as_sf(coords = c("longitude", "latitude"), crs = 4326, remove = FALSE)
}

pb_layers <- purrr::map(
  pb_file_index_window$file,
  read_pb_particle_file
)

pb_all <- dplyr::bind_rows(pb_layers) %>% sf::st_drop_geometry()

pb_labels <- pb_file_index_window$display_label
pb_group_names <- paste0("pb-hour-", seq_along(pb_layers))

map_date_label <- if (!all(is.na(params$BURN_DATE))) {
  as.character(params$BURN_DATE)
} else {
  format(min(pb_file_index_window$file_date_local, na.rm = TRUE), "%Y-%m-%d")
}

map_title <- paste0(
  "PB Piedmont Output for ",
  params$BURN_NAME,
  " • ",
  params$FOREST,
  " [",
  map_date_label,
  "]"
)

caution_html <- HTML("Please note: for internal use only.<br>Do not distribute outside of USFS.")
```


<style>
body {
  margin: 0;
  padding: 0;
}

.main-container {
  max-width: none !important;
  width: 100% !important;
  padding: 0 !important;
}

h1.title {
  display: none;
}

.pb-header-banner {
  display: flex;
  align-items: center;
  gap: 18px;
  margin: 0;
  padding: 18px 24px;
  background: linear-gradient(90deg, #032B5B 0%, #0B3D73 100%);
  border-bottom: 5px solid #F28C28;
  box-shadow: 0 2px 10px rgba(0,0,0,0.22);
}

.pb-header-banner img {
  width: 78px;
  height: 78px;
  border-radius: 16px;
  background: rgba(255,255,255,0.96);
  padding: 6px;
  object-fit: contain;
  box-shadow: 0 2px 8px rgba(0,0,0,0.28);
}

.pb-header-text {
  display: flex;
  flex-direction: column;
}

.pb-header-main {
  color: white;
  font-size: 34px;
  font-weight: 800;
  line-height: 1.05;
  margin: 0;
}

.pb-header-sub {
  color: rgba(255,255,255,0.88);
  font-size: 18px;
  margin-top: 6px;
  line-height: 1.25;
  font-weight: 700;
}

.pb-header-date {
  color: rgba(255,255,255,0.78);
  font-size: 15px;
  margin-top: 5px;
  line-height: 1.25;
}

.leaflet-container {
  width: 100% !important;
  height: calc(100vh - 125px) !important;
}

.leaflet-control.map-title {
  color: red;
  text-align: left;
  padding: 8px 10px;
  background: rgba(255,255,255,0.75);
  font-weight: bold;
  font-size: 20px;
  border-radius: 4px;
  clear: none !important;
  margin-left: 8px !important;
  margin-top: 10px !important;
}

/* Keep the disclaimer to the right of the +/- zoom buttons. */
.leaflet-left .leaflet-control.map-title {
  float: left !important;
}

.burn-fire-icon {
  width: 30px !important;
  height: 30px !important;
  border-radius: 50%;
  overflow: hidden;
  background: rgba(255,255,255,0.92);
  border: 1px solid rgba(0,0,0,0.35);
  box-shadow: 0 1px 4px rgba(0,0,0,0.35);
}

.burn-fire-icon img {
  width: 24px !important;
  height: 24px !important;
  margin: 3px;
  object-fit: contain;
}

.pb-slider-control {
  background-color: rgba(255,255,255,0.88);
  color: black;
  font-family: Open Sans, sans-serif;
  font-weight: bold;
  padding: 8px 16px 12px 16px;
  border-radius: 5pt;
  box-shadow: 0pt 0pt 6pt 0px rgba(61,59,61,0.48);
  min-width: 340px;
}

.pb-slider-title {
  margin-bottom: 3px;
}

.pb-slider-label {
  font-size: 13px;
  margin-bottom: 4px;
}

.pb-slider-control input[type='range'] {
  width: 300px;
}

.pb-slider-row {
  display: flex;
  align-items: center;
  gap: 8px;
}

.pb-step-button {
  width: 34px;
  height: 30px;
  border: 1px solid #b8c5cf;
  border-radius: 6px;
  background: #032B5B;
  color: white;
  font-weight: 800;
  line-height: 1;
  cursor: pointer;
}

.pb-step-button:hover {
  background: #0B3D73;
}

.pb-step-button:disabled {
  background: #c9d2da;
  border-color: #c9d2da;
  cursor: not-allowed;
}
</style>

```{r pb_browser_title, results='asis', echo=FALSE}
cat(
  paste0(
    "<script>",
    "document.addEventListener('DOMContentLoaded', function() {",
    "document.title = ",
    jsonlite::toJSON(map_title, auto_unbox = TRUE),
    ";",
    "});",
    "</script>"
  )
)
```

```{r pb_banner, results='asis', echo=FALSE}
cat(
  paste0(
    "<div class='pb-header-banner'>",
      "<img src='", pb_icon_uri, "' alt='PB Piedmont Fog Icon'>",
      "<div class='pb-header-text'>",
        "<div class='pb-header-main'>",
          htmltools::htmlEscape(params$BURN_NAME),
          " • ",
          htmltools::htmlEscape(params$FOREST),
        "</div>",
        "<div class='pb-header-sub'>PB Piedmont Output</div>",
        "<div class='pb-header-date'>",
          htmltools::htmlEscape(map_date_label),
        "</div>",
      "</div>",
    "</div>"
  )
)
```


```{r map, out.width='100%'}
# Build a deterministic one-hour-at-a-time canvas map.
# This more closely matches the old Shiny app behavior:
#   filteredData() %>% filter(start_time == input$date[1])
# and then redraws all particles for that selected timestep.

pb_hour_payload <- purrr::map(
  pb_file_index_window$file,
  function(file) {
    readr::read_table(file, show_col_types = FALSE) %>%
      transmute(
        longitude = as.numeric(longitude),
        latitude = as.numeric(latitude),
        fog = as.integer(fog),
        color = if_else(fog == 1, "darkred", "goldenrod")
      ) %>%
      filter(!is.na(longitude), !is.na(latitude), !is.na(fog))
  }
)

pb_map <- leaflet(options = leafletOptions(preferCanvas = TRUE)) %>%
  addProviderTiles(providers$OpenStreetMap.Mapnik, group = "Street") %>%
  addProviderTiles("Esri.WorldImagery", group = "Terrain") %>%
  fitBounds(
    lng1 = min(pb_all$longitude, na.rm = TRUE),
    lat1 = min(pb_all$latitude, na.rm = TRUE),
    lng2 = max(pb_all$longitude, na.rm = TRUE),
    lat2 = max(pb_all$latitude, na.rm = TRUE)
  ) %>%
  addLegend(
    "bottomleft",
    colors = c("darkred", "goldenrod"),
    labels = c("Fog", "Smoke"),
    title = "Particle Type",
    opacity = 0.6
  ) %>%
  addScaleBar(position = "bottomright", options = scaleBarOptions(metric = FALSE)) %>%
  addLayersControl(baseGroups = c("Street", "Terrain")) %>%
  addControl(caution_html, position = "topleft", className = "map-title") %>%
  addMarkers(
    data = burn_info,
    lng = ~lon,
    lat = ~lat,
    icon = leaflet::makeIcon(
      iconUrl = fire_icon_uri,
      iconWidth = 30,
      iconHeight = 30,
      iconAnchorX = 15,
      iconAnchorY = 15
    )
  )

pb_map %>%
  htmlwidgets::onRender(
    "
    function(el, x, data) {
      var map = this;
      var currentIndex = 0;
      var canvasRenderer = L.canvas({padding: 0.5});
      var particleLayer = L.layerGroup().addTo(map);

      // Keep the burn icon square/round instead of stretched tall.
      setTimeout(function() {
        var markerImgs = el.querySelectorAll('img.leaflet-marker-icon');
        markerImgs.forEach(function(img) {
          img.style.width = '30px';
          img.style.height = '30px';
          img.style.borderRadius = '50%';
          img.style.objectFit = 'contain';
          img.style.background = 'rgba(255,255,255,0.92)';
          img.style.border = '1px solid rgba(0,0,0,0.35)';
          img.style.boxShadow = '0 1px 4px rgba(0,0,0,0.35)';
          img.style.padding = '3px';
        });
      }, 0);

      function getPointCount(pts) {
        if (Array.isArray(pts)) return pts.length;
        if (pts && Array.isArray(pts.longitude)) return pts.longitude.length;
        return 0;
      }

      function getPoint(pts, i) {
        if (Array.isArray(pts)) return pts[i];
        return {
          longitude: pts.longitude[i],
          latitude: pts.latitude[i],
          color: pts.color[i]
        };
      }

      function redrawParticles(index) {
        particleLayer.clearLayers();
        var pts = data.hours[index] || [];
        var n = getPointCount(pts);

        for (var i = 0; i < n; i++) {
          var p = getPoint(pts, i);
          L.circleMarker([p.latitude, p.longitude], {
            renderer: canvasRenderer,
            radius: 3.5,
            stroke: false,
            fill: true,
            fillColor: p.color,
            fillOpacity: 0.72,
            interactive: false
          }).addTo(particleLayer);
        }

        currentIndex = index;
        var label = document.getElementById('pb-label-' + el.id);
        if (label) {
          label.innerHTML = data.labels[index];
        }
      }

      var sliderControl = L.control({position: 'bottomleft'});

      sliderControl.onAdd = function(map) {
        var div = L.DomUtil.create('div', 'pb-slider-control leaflet-bar');
        div.innerHTML = `
          <div class='pb-slider-title'>Time step (hour)</div>
          <div class='pb-slider-label' id='pb-label-${el.id}'></div>
          <div class='pb-slider-row'>
            <button type='button' class='pb-step-button' id='pb-prev-${el.id}' aria-label='Previous time step'>&#9664;</button>
            <input id='pb-slider-${el.id}' type='range' min='0' max='${data.hours.length - 1}' value='0' step='1'>
            <button type='button' class='pb-step-button' id='pb-next-${el.id}' aria-label='Next time step'>&#9654;</button>
          </div>
        `;

        L.DomEvent.disableClickPropagation(div);
        L.DomEvent.disableScrollPropagation(div);
        return div;
      };

      sliderControl.addTo(map);

      var slider = document.getElementById('pb-slider-' + el.id);
      var prevButton = document.getElementById('pb-prev-' + el.id);
      var nextButton = document.getElementById('pb-next-' + el.id);

      function setStep(index) {
        var maxIndex = data.hours.length - 1;
        var newIndex = Math.max(0, Math.min(maxIndex, index));

        slider.value = newIndex;
        redrawParticles(newIndex);

        if (prevButton) prevButton.disabled = newIndex === 0;
        if (nextButton) nextButton.disabled = newIndex === maxIndex;
      }

      slider.addEventListener('input', function(e) {
        setStep(parseInt(e.target.value));
      });

      slider.addEventListener('change', function(e) {
        setStep(parseInt(e.target.value));
      });

      prevButton.addEventListener('click', function(e) {
        e.preventDefault();
        setStep(parseInt(slider.value) - 1);
      });

      nextButton.addEventListener('click', function(e) {
        e.preventDefault();
        setStep(parseInt(slider.value) + 1);
      });

      setStep(0);
    }
    ",
    data = list(
      hours = pb_hour_payload,
      labels = pb_labels
    )
  )
```

